
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\usepackage{hyperref}

\name{Sathish Sekar} % Your name
%\address{123 Broadway \\ City, State 12345} % Your address
\address{4302 College Main, \#117, Bryan, TX 77801 \\ (979)-739-8232 \\ ssathish261990@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}{Masters of Computer Engineering}{\em Fall 2013 - Summer 2015}{Texas A\&M University}{College Station, TX, USA}
\item {\bf CGPA:} 3.67/4.0
\end{rSubsection}

\begin{rSubsection}{B.E in Computer Science \& Engineering}{\em August 2007 - April 2011}{College of Engineering, Anna University}{Chennai, Tamil Nadu, India}
\item {\bf CGPA:} 8.58/10.0
\end{rSubsection}


\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Renault Nissan Technology and Business India Pvt. Ltd.}{July 2011 - July 2013}{Software Engineer}{Chennai, India}
\item Developed a web application in Sales and Marketing domain to handle post sale issues for Renault Automobile customers worldwide.
This was developed using {\bf Struts Framework}.
\item Developed and deployed web services for internal Renault applications.
\item Designed and developed custom Data Loader application in JAVA which used BULK API of Salesforce.com for performing routine data loading and sync activities between Salesforce.com and local MySQL database.
\end{rSubsection}

%------------------------------------------------

\end{rSection}

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & C, C++, Java, Octave \\
Web Programming & HTML, JSP, JavaScript, PHP, CSS \\
Protocols \& APIs & XML, SOAP, BULK API for SalesForce.com \\
Databases & Oracle, MySQL \\
Libraries & OpenCV for Computer Vision, OpenGL for Graphic Design \\
Frameworks & Struts for JAVA \\
Tools & IBM RAD, Rational Rose, SVN, Maven, GitHub \\
Servers & IBM Websphere 6.1, JBoss AS 7.1, XAMPP, WAMP \\
OS & Linux, Windows \\
Others & Adobe Dreamweaver, Adobe Photoshop 4, Microsoft Office
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Experience}

\begin{rSubsection}{Interactive Palm display system for ubiquitous environment }{Dec 2010 - Apr 2011}{Implemented using OpenCV Library for C++}
\item A system comprising a mini projector, a video recording device and a mobile computing device that enables the user to interact with a GUI object projected on his palm, using his fingertip. Detection of palm, fingertip, projected GUI objects and touch form the core components of this project. The system is implemented without the use of colored marker worn on fingertip. An algorithm to detect contour for identifying fingertip and a shadow based technique to sense touch was developed.

\item \textit{Sekar, S., S.K. Vasudevan, K. Velusamy, Y.M. Purohit and G. Alagappan et al., 2014. Ubiquitous palm display and fingertip tracker system using opencv. J. Comput. Sci., 10: 382-392.} 

\textit{http://thescipub.com/pdf/10.3844/jcssp.2014.382.392}

\end{rSubsection}

%------------------------------------------------


\end{rSection}

\clearpage

%----------------------------------------------------------------------------------------
%	INTERNSHIP EXPERIENCE SECTION
%----------------------------------------------------------------------------------------



%------------------------------------------------




%----------------------------------------------------------------------------------------
%	ACADEMIC PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Academic Projects}

\begin{rSubsection}{Dynamic Bandwidth Controller}{August 2013}
{Implemented using BSD sockets API in C++}{}
\item Implemented a dynamic bandwidth controller that allows users to prioritize their downloads by assigning individual bandwidth limits for each download. 
\end{rSubsection}

\begin{rSubsection}{Falling Balls Game}{Jan 2010}
{Interactive Single Player Game implemented using OpenGL kit for C}{}
\item A stick figure has to move horizontally to avoid falling balls. Implemented an algorithm to control the size, position and speed of falling balls as the game progresses.
\end{rSubsection}


\begin{rSubsection}{Seminar Hall booking system}{July 2009}
{Web Application Implemented using PHP, MySQL and XAMPP server}{}
\item Developed an intranet web application that helps students and teaching faculty to book seminar halls available in my department. Mail alerts and Chat feature were also implemented. 
\end{rSubsection}

\begin{rSubsection}{Traffic Controller Simulator}{Jan 2008}
{Implemented using Hardware Descriptor Language}{}
\item Implemented an automatic traffic controller that efficiently routes traffic and alternatively adapts to a situation where a manual user controls partial traffic. Implemented the algorithm for a specific set of
road structures.
\end{rSubsection}

\begin{rSubsection}{9X9 Sudoku Solver}{July 2008}
{Interactive Sudoku Solver implemented using C++}{}
\item Implemented an algorithm that can solve 9X9 Sudoku puzzles based on the number of available input numbers and their positions.
\end{rSubsection}

%------------------------------------------------


\end{rSection}

\begin{rSection}{Git Profile}
\item \textit{https://github.com/SattyS}
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------




%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
